---
title: "SeuratObject Benchmark Notebook"
output:
  html_document: default
  pdf_document: default
---


Libraries needed for Seurat Object
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(Seurat)
library(patchwork)
library(bench)
```

Load the PBMC dataset. The data consists in 3k PBMCs from a Healthy Donor and is freely available from 10x Genomics.

```{r}
# Load the PBMC dataset
pbmc.data <- Read10X(data.dir = "./data/pbmc3k/filtered_gene_bc_matrices/hg19/")

# Initialize the Seurat object with the raw (non-normalized data)
pbmc <- CreateSeuratObject(counts = pbmc.data, project = "pbmc3k", min.cells = 3, min.features = 200)
```

The PBMC Seurat Object
```{r}
pbmc
```

Normalize the data with "LogNormalize" method (default)
```{r}
pbmc <- NormalizeData(pbmc)
```


```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst", nfeatures = 2000)
```

Scale the data
```{r}
pbmc <- ScaleData(pbmc)
```

Perform PCA (Linear Dimensionality Reduction)
```{r}
pbmc <- RunPCA(pbmc, features = VariableFeatures(object = pbmc))
```

```{r, time_it = TRUE}
head(pbmc)
```

Memory allocation for the subset expression where nCount_RNA is greater than 1000
```{r}
bnch <- bench::mark(
        subset(x = pbmc, subset = nCount_RNA > 1000)
        )
bnch
```

Cluster the cells
```{r}
pbmc <- FindNeighbors(pbmc, dims = 1:10)
pbmc <- FindClusters(pbmc, resolution = 0.5)
```

Memory allocation for the same subset after Clustering

```{r}
bnch_cluster <- bench::mark(
        subset(x = pbmc, subset = nCount_RNA > 1000)
        )
bnch_cluster
```


